\prefacesection{Quacknowledgments}
I would like to express my deepest gratitude to my colleagues, friends, and
family who have influenced and supported my growth throughout graduate school.

First, I would like to thank my co-advisors---Keith Winstein, David Mazières,
and Matei Zaharia. Keith has this gift for storytelling that has become a model
for how I want to communicate to the world. I have learned so much from him,
and feel so grateful for the series of events that brought us together. David
and Matei were especially influential in the early years of my PhD. David
exudes this idealism that motivates me to pursue ambitious goals and stay true
to my values. Matei has a unique penchant for anticipating how an idea will be
received, evolve, and ultimately make an impact, inspiring me to select
problems with the same intentionality. My co-advisors have been a constant
source of confidence and support, and I am deeply grateful for their
mentorship.

I cannot express enough gratitude for the guidance I have received---I am
honored to have worked with Michael Welzl, who has sparked so much joy over the
years with his passion, knowledge, and excitement about the Internet. The
theoretical foundations of this work owe much to the mentorship of Dan Boneh
and Mary Wootters. I am thankful for Kate Maher, my orals
committee chair. I'd also like to extend my appreciation to Te-Yuan Huang, Wei Wei,
Yiannis Yiakoumis, Bruce Spang, Deian Stefan, Robert Morris, Malte Schwarzkopf,
Jon Gjengset, Raul Castro Fernandez, and Albert Carter.

This work would not have been possible without Matthew Sotoudeh and David Zhang,
whose unique perspectives on research provided just the inspiration needed to
connect the dots during a more stagnant period of my PhD. Thea Rossman became
my networking compatriot in my final year, and I am thankful for our many
brainstorming sessions throughout our lively collaboration. It was also my
pleasure to work with these bright undergraduates---Devrath Iyer, Jaylene
Martinez, Angel Rivera, Henry Weng---who shaped the way that I approach
mentorship.

I am thankful for my labmates in Stanford SNR, Stanford SCS, and the FutureData
group for the welcoming and vibrant sense of community---Yuhan Deng, Akshay
Srivatsan, Colin Drewes, Yasmine Mitchell, Francis Chua, Sebastian Ingino,
Angie Montemayor, Geoffrey Ramseyer, Zachary Yedidia, Firas Abuzaid, Lingjiao
Chen, Cody Coleman, Jared Quincy Davis, Trevor Gale, Daniel Kang, Fiodar
Kazhamiaka, Omar Khattab, Peter Kraft, Qian Li, Deepak Narayanan, Shoumik
Palkar, Liana Patel, Deepti Raghavan, Kexin Rong, Sahaana Suri, Keshav
Santhanam, Kai Sheng Tai, Pratiksha Thaker, James Thomas. I want to extend my
special thanks to Deepti, Deepak, and Shoumik, senior student mentors and
co-authors whose wisdom and humility I hope to carry on.

Thank you to many others in the Stanford community who have impacted me in some
way---the systems and security communities, Aishwarya Mandyam and the Race
Condition Running club, the friends I have made through the Stanford Cycling
community including Miles Chan, Jack Liu, Claire MacDougall, Basil Saeed, Paddy
Simha, Albert Wu, and coaches Adrian Bennett and Isaiah Newkirk.

During the pandemic when I had nowhere to go but outdoors, I picked up road
cycling, raced bikes, and met some awesome people---Niky Taylor, Kelly
Brennan, and Chloé Mauvais. Our relationships with bikes have evolved over time
but our friendships have not. I poured my heart into Alto Velo, and it meant a
lot to me to have grown this community with some amazing women---Sue Lin Holt,
Robin Betz, Ari Fischer, Emily Schell, Louise Thomas, Steph Hart, Rachel Hwang,
Katie Monaghan.

Fully grasping that the Internet didn't exist when my parents were born has made
me all the more impressed with their story---immigrating to the U.S., building
careers as software engineers, and quietly inspiring Paula and me to pursue
computer science. I am secretly thrilled that the four of us are reunited in
the Bay Area. I also want to express deep respect for my grandma, Weijiu Zhang,
whose memory deepens my appreciation for life and the sacrifices that came
before me. Thank you to my parents, Christine Lei and Wei Yuan, for creating
the opportunities for me to chase my dreams.

Finally, I feel incredibly lucky to have been able to grow alongside my partner,
Jack Liu. His curiosity, spontaneity, and dedication to his pursuits encourage
me to approach my own work and life with the same vigor. Thank you for all the
happiness and random treats you bring to my life.
