\section{Introduction}
\label{sec:sidekick:intro}

In the Internet's canonical model, transport is end-to-end and implemented only
in hosts; only hosts think about connections, reliable delivery, or
flow-by-flow congestion control (\Cref{sec:introduction}).
In practice, however, the best behavior for a
transport protocol depends on the particulars of the network path. An
appropriate retransmission or congestion-control scheme for a
heavily-multiplexed wired network wouldn't be ideal for paths that include a
high-delay satellite link, Wi-Fi with bulk ACKs and frequent reordering, or a
cellular WWAN~\cite{kuhn2021quic-over-sat,goyal2017abc}.

By the 1990s, many networks had broken from the canonical model by deploying
in-network TCP accelerators, also known as ``performance-enhancing proxies''
(PEPs)~\cite{rfc3135}. TCP PEPs can split an end-to-end connection into
multiple concatenated connections~\cite
{kapoor2005achieving,caini2006pepsal,davern2011httpep,farkas2012splittcp,hayes2019mmwave},
buffer and retransmit packets over a lossy link~\cite
{balakrishnan1995snoop,polese2017milliproxy}, virtualize congestion
control~\cite{cronkite2016vcc,he2016acdc,mihaly2012mobilePEP}, resegment the
byte stream, and enable forward error correction, ECN,
or other segment-specific enhancements. Because TCP isn't
encrypted or authenticated, PEPs can achieve this without the
knowledge or cooperation of end hosts. Roughly 20--40\% of Internet paths cross
at least one TCP PEP~\cite{honda2011still, edeline2019bottomup}.

While many flows benefit from PEPs, their use carries a cost: protocol
ossification~\cite{papastergiou2017deossifying, edeline2019bottomup}.
% When a
% middlebox inserts itself in a connection and enforces its preconceptions about
% the transport protocol, it can thwart the protocol's evolution, dropping
% traffic that uses an upgraded version or new options. TCP PEPs have hindered or
% complicated the deployment of many TCP improvements, such as ECN++, tcpcrypt,
% TCP extended options, and Multipath TCP~\cite
% {mandalari2018ecnplusplus,honda2011still,raiciu2012multipathtcp}.
In response,
% to this ossification, and to an increased emphasis on privacy and security,
post-TCP transport protocols have been designed to be impervious to
meddling middleboxes by encrypting and authenticating the transport header. We
refer to these newer transport protocols as ``opaque'' transport protocols. The
most prevalent is QUIC~\cite{rfc9000}, found in billions of installed Web
browsers and millions of servers~\cite{zirngibl2021quicdeployment}; other secure
transport protocols are used in WebRTC/SRTP~\cite{rfc8834webrtc},
Zoom~\cite{zoom}, BitTorrent~\cite{bittorrent}, and
Mosh/SSP~\cite{winstein2012mosh}.

This opacity means that middleboxes can't interpose themselves on a
connection or understand the sequence numbers of packets in transit. This
prevents PEPs from providing assistance, in some situations reducing the
performance of opaque transport protocols~\cite
{border2020quicsat-presentation,kuhn2021quic-over-sat,martin2022suitability,border2020evaluating,kosek2022quicpep}.
It's possible to co-design protocols and PEPs to permit assistance from
credentialed middleboxes~\cite{ford2008logjam,sherry2015blindbox, dogar2012tapa,iyengar2009flow},
but challenging to do so without tightly coupling these components and risks
ossification and fragility. The resulting tension between the performance
enhancements of PEPs and protocol ossification makes it challenging to provide
in-network assistance to secure transport protocols.

In this chapter, we propose a
second protocol called the \emph{\bf Sidekick protocol} to be spoken on an
adjacent connection between an end host and a PEP. The contents of the adjacent
connection are \emph{about} the packets of the underlying ``base'' connection.
Sidekick proxies assist end hosts by reporting what they've observed about the
packets of the encrypted base connection, leaving the transport protocol
unchanged on the wire: an encrypted end-to-end connection between hosts, opaque
to middleboxes and free to evolve. End hosts use this information to influence
decisions about how and when to send packets on the base connection,
approximating some of the performance benefits of traditional PEPs.
No PEPs are credentialed to decrypt the transport protocol's headers.

% Instead, we propose a second protocol to be spoken on an adjacent connection
% between an end host and a PEP. We call this the \emph{\bf Sidekick protocol},
% and its contents are \emph{about} the packets of the underlying, or ``base,''
% connection.
% Sidekick PEPs assist end hosts by reporting what they've observed
% about the packets of the encrypted base connection, without coupling their
% assistance to the details of the base protocol. End hosts use this information
% to influence decisions about how and when to send or resend packets on the base
% connection, approximating some of the performance benefits of traditional PEPs.
% We first proposed a similar functional separation in \cite{yuan2022sidecar},
% and presented a concrete realization of the idea and its nuanced
% interactions with real transport protocols in \cite{yuan2024sidekick}.

One key technical challenge in this approach is how Sidekick proxies can
efficiently refer to a set of packets in an encrypted base connection when
these packets appear random to the middlebox. Referring to a range of, say, 100
encrypted packets in the presence of loss and reordering is not as simple as
saying ``up to 100'' in the case of packets with cleartext sequence numbers. To
solve this problem, we leverage the power sum quACK from \Cref{sec:quack}. The
{\bf quACK} is a mathematical tool that concisely represents a selective
acknowledgment of encrypted packets when there is a practical bound on the
maximum number of ``holes'' among the packets being ACKed.

A second challenge is how the end host should use information from a Sidekick
proxy to obtain a performance benefit for its base connection. Since the
performance benefit comes from changing behavior at the end host rather than
the middlebox, transport protocols need to incorporate this information into
their existing algorithms for, e.g., loss detection and retransmission, which
have gotten increasingly complex over time. To explore this, we designed a
Sidekick protocol and integrated it into client implementations with path-aware
modifications in three scenarios:
\begin{itemize}[noitemsep,topsep=2pt]
\item A low-latency audio stream over an Internet path that includes a lossy,
  low-latency Wi-Fi path segment, followed by a reliable, higher-latency WAN
  path segment. Can using the Sidekick protocol reduce the de-jitter buffer
  delay by triggering earlier retransmissions on loss?

\item An upload over the same path. Can a secure transport protocol like QUIC,
  aided by a Sidekick proxy at the point between these two path segments, match
  the throughput of TCP over a connection-splitting PEP?

\item A battery-powered receiver downloading data from the Internet over Wi-Fi.
  If the Wi-Fi access point sends quACKs over a Sidekick connection on behalf of
  the receiver,
  can it reduce the number of times the receiver's radio needs to wake up
  to send an end-to-end ACK?
\end{itemize}

\smallskip

A third technical challenge is how knowledge about \emph{where}
loss occurs along a path should influence a congestion-control scheme.
The challenge in any such scheme is how to maximize the congestion window
to achieve high throughput
while sharing the network fairly with competing flows.
We present a path-aware modification to the CUBIC congestion-control
algorithm~\cite{ha2008cubic}, which we call \mbox{\textbf{PACUBIC}},
that approximates the congestion-control behavior of a PEP-assisted split TCP
CUBIC connection while making its decisions entirely on the host.

\paragraph{Summary of results.}

We evaluated the three scenarios above, integrating the Sidekick protocol with a
media client based on the WebRTC standard and an HTTP/3 client using
\texttt{libcurl} and the Cloudflare implementation of QUIC~\cite{quiche}.
In real-world experiments using an unmodified local Wi-Fi network to access our
nearest AWS datacenter, the Sidekick proxy was able to trigger early retransmissions
to fill in gaps in the audio of a latency-sensitive audio stream, reducing the
receiver's de-jitter delay from 2.3~seconds to 204~ms---about a 91\% reduction
(\Cref{fig:sidekick:real-world}). The Sidekick proxy was also able to improve the
speed of an HTTP/3 (QUIC) upload by about 50\%.

In emulation experiments of the ``battery-powered receiver'' scenario,
the Sidekick proxy was able to reduce the need for the receiver to send ACKs
by sending proxy acknowledgments on its behalf---ACKs the sender used
to advance its flow-control and congestion-control windows. The
receiver only needed to wake up its radio to send occasional
end-to-end ACKs, which the sender used to discard data from its
buffer (\Cref{fig:sidekick:main-results:ack-reduction}).

Also in an emulation experiment, we confirmed that PACUBIC's achieved throughput
approximates that of a split CUBIC connection (two TCP CUBIC
connections separated by a PEP), responding to loss events proportionally to
the delay of the path segment on which the loss occurs
(\Cref{fig:sidekick:fairness-line}). The results indicate that the gains from
using the Sidekick protocol do not come at the
expense of congestion-control fairness relative to a split CUBIC connection.\\

\noindent
The rest of this chapter discusses the three motivating scenarios for Sidekick
protocols in more detail (\Cref{sec:sidekick:motivating}). We describe the
concrete Sidekick protocol and path-aware sender modifications we built around
power sum quACKs (\Cref{sec:sidekick:design}), including path-aware CUBIC
congestion control (\Cref{sec:sidekick:pacubic}) and its integrations with two
base protocols (\Cref{sec:sidekick:implementation}). We evaluate
(\Cref{sec:sidekick:methodology}) the use of the protocol in real-world
(\Cref{sec:sidekick:real-world}) and emulation experiments
(\Cref{sec:sidekick:emulation}). Finally, we discuss limitations to our approach
(\Cref{sec:sidekick:limitations}) and conclude (\Cref{sec:sidekick:summary}).
