\section{Limitations}

The \sys approach, and our experiments, are subject to some
limitations, which we describe briefly here.

\paragraph{Multipath scenarios.}
We have only considered \sys proxies along a single path, and not thought
extensively about how quACKs would interact with protocols such as
\mbox{TCPLS}~\cite{rochet2020tcpls} that use multiple paths or streams,
or even multipath QUIC~\cite{de2017multipath}.
To begin thinking about this question, we would have a more complex model of
the network: multiple PEPs along a single path, multiple paths each with varying
numbers of PEPs, and so on. The proxy can include
additional information in the \sys-reply packet to indicate which path the
PEP assistance is on, and the sender can infer from the RTT how far along a path each PEP
is relative to others. New \sys algorithms that come from this model could
diagnose troublesome paths, or better allocate network traffic in a multipath
connection. Existing algorithms could be applied to individual paths as if they
were single-path connections.

\paragraph{Even more diverse network scenarios.}
The three scenarios we explored all consisted of a lossy Wi-Fi link and a
high-latency WAN link. Not all scenarios will be favorable to the
\sys protocol we designed.
If the ``lossy'' section of a network path were on the far path segment from the
sender, the sender would not have any more information about the problematic
link. To accomodate scenarios like this, \sys protocols will need
more features. For example, the \emph{proxy} would need some way to receive
quACKs from the data \emph{receiver}, as well as a mechanism to buffer and
retransmit packets~\cite{balakrishnan1995snoop,caini2006pepsal}.

There are likely other scenarios that could benefit from \sys protocols as
described, but we did not evaluate them. For example, if we replaced the lossy Wi-Fi
link with a modern wireless link that has a fluctuating physical
capacity~\cite{niu2015survey,burchardt2014vlc,koenig2013wireless},
the sender may be able to more quickly adapt and make
data available for transmission whenever capacity intermittently becomes available.
% More dynamic real-world evaluations, such as actually riding a train, will be
% needed to characterize the practical improvement that {\sys}s can yield in
% true real-world situations.

% \paragraph{Overheads at \sys proxies aren't trivial.}

% Computing quACKs is inexpensive and plausible for a Wi-Fi access point---less
% than 200~ns/pkt on a commodity CPU, or $\approx$2.5~Gbit/s per core in software.
% But \Cref{tab:cpu-overhead} shows that, at
% least in our current software implementation, vastly greater overhead
% comes just from \emph{maintaining per-flow state}
% accessed on a per-packet basis. To make \sys
% proxies feasible on affordable devices, this will need to be accelerated.


\paragraph{Practical deployment.}

The implementation of Robin exists as a research system that has been evaluated
in emulation and a limited set of real-world scenarios. Since \sys protocols
require the cooperation of middleboxes and client applications, more work will
be needed to standardize the discovery protocol and wire format of \sys messages
described in \Cref{sec:design}, ideally with interest from the IETF.
The standards will need to establish several design choices such as how
identifiers are computed, how quACKs are transmitted, and the exact mechanisms
for security and backwards compatibility.
We may also want to standardize sender behavior for specific base protocols,
though this could be opaque except to the sender.

The deployment of \sys protocols can be gradual and backwards-compatible
with parties that are either unaware of or do not want to participate in \sys
protocols.
To migrate existing client applications, one needs to modify the code to
discover a PEP and use information in a quACK to inform the base protocol.
To migrate middleboxes, they would need to be modified to listen for
\sys-request markers, then accumulate and send quACKs for participating
connections.


\paragraph{Deeper analysis of path-aware congestion control.}

The correspondence between endpoint-driven PACUBIC and ``split CUBIC''
is good, and both are better than end-to-end CUBIC in
\Cref{fig:loss-vs-tput}), but not exact. The appropriateness of the
PACUBIC heuristic, and in general the idea of path-aware congestion
control, needs to be further explored. We discuss this more in
\Cref{sec:appendix:pacubic}.

